Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
paper: fix fig 1
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

@@

\subsection{ZLog: A Fast Distributed Shared-Log}

@@

\subsubsection{Sequencer}

@@

@@

Mantle is used to implement a zlog file type specific policy for maximizing
throughput to the sequencer by migration the resource between metadata servers.

Sequencer recovery is handled by tapping into existing recovery mechanisms
that recover inode state. file type specific recovery augments the existing
recovery procedure.

>>>>

\begin{figure}[tb]
\centering
\includegraphics{figures/overview.png}
\caption{A Ceph installation consists of a cluster running mostly
storage daemons (OSDs) to ensure data durability, a few monitor daemons
(MONs) to reach consensus of the cluster state and to ensure its
consistent versioning, and a few metadata service daemons (MDSs) for
scalable metadata service. Ceph's APIs include object, block, file
abstractions. Malacology enables the programmability of these
abstractions and services (indicated by bold arrows). To illustrate Malacology we implement two
services on Ceph, Zlog and Mantle, by programming Ceph's durability,
consistent versioning, consensus, and metadata subsystems.
\label{fig:overview}}
\end{figure}

@@

\subsection{ZLog: A Distributed Shared-Log}

@@

@@

\subsubsection{Sequencer recovery with
MDS}\label{sequencer-recovery-with-mds}

\subsubsection{MDS Policy for Revoking
Capability}\label{mds-policy-for-revoking-capability}

@@

\subsubsection{Mantle Balancing Policies to Migrate
Sequencers}\label{mantle-balancing-policies-to-migrate-sequencers}
